% !TEX root = sbaconf.tex
%===============================================================================
% $Id: ifacconf.tex 19 2011-10-27 09:32:13Z jpuente $  
% Template for IFAC meeting papers
% Copyright (c) 2007-2008 International Federation of Automatic Control
%===============================================================================
\documentclass[a4paper]{ifacconf}

\usepackage{graphicx,amsmath,url}      % include this line if your document contains figures
\usepackage[round]{natbib}             % required for bibliography
%===============================================================================

% If in Portuguese or Spanish, choose
\def\portugues{1} 
\usepackage[spanish,brazil,english]{babel}
\usepackage[T1]{fontenc}
%\usepackage[utf8]{inputenc}
\usepackage{unicode}
\usepackage{ae}
\usepackage{placeins}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{cuted}
\usepackage{amsmath} % for 'bmatrix' environment
\newcommand\norm[1]{\left\lVert#1\right\rVert}
\newcommand\normx[1]{\left\Vert#1\right\Vert}
\newcommand\Hinfty{\mathcal{H}_\infty}
\newcommand\Hdois{\mathcal{H}_2}
\newcommand\Ldois{\mathcal{L}_2}
\newcommand\ms{290}
\newcommand\mus{40}
\newcommand\bls{700}
\newcommand\bnls{200}
\newcommand\bys{400}
\newcommand\kls{235\cdot10^2}
\newcommand\knls{235\cdot10^4}
\newcommand\kt{190\cdot10^3}
        
 
\if\portugues1
% =====================================================================
% =====================================================================
% If the manuscript is in Spanish, please change the texts adequatelly.
% You may also add other definitions in this part.
 \newtheorem{teorema}[thm]{{\em Teorema}}{ }
 \newtheorem{lema}[thm]{{\em Lema}}{ }
 \newtheorem{corolario}[thm]{{\em Corolário}}{ }
 \newenvironment{prova}{{\bf Prova.}}{ }
% ===============================================================
\fi

\begin{document}
	
    \selectlanguage{brazil}
	
    \begin{frontmatter}
        
        \title{Síntese de observador e controlador por realimentação de estados para controle de suspensão veicular ativa, não-linear} 

        \author[First]{Charles Quirino Pimenta} 
        
        \address[First]{Programa de Pós-Graduação em Engenharia Elétrica - Universidade Federal de 
Minas Gerais - Av. Antônio Carlos 6627, 31270-901, Belo Horizonte, MG, Brasil\\ e-mail:charlesqp@ufmg.br.}
        
        \selectlanguage{english}
        \renewcommand{\abstractname}{{\bf Abstract:~}}
        \begin{abstract} This work presents a synthesis methodology of a state-feedback controller and an observer for time-invariant linear systems, in addition to evaluating their performance through temporal simulations. A non-linear system extracted from the literature was chosen, an active vehicle suspension model for a quarter of a car. In this system, the non-linearities are present in the springs and in the damper. The synthesis conditions were programmed, simulated and evaluated in Matlab\textsuperscript{\textregistered} environment. The temporal simulation results were presented and at the end a brief conclusion is presented.
        
        \vskip 1mm% não altere esse espaçamento
        \selectlanguage{brazil}
        {\noindent \bf Resumo}: Este trabalho apresenta uma metodologia de síntese de um controlador por realimentação de estados e um observador para sistemas lineares invariantes no tempo além de avaliar o seu desempenho por meio de simulações temporais. Foi escolhido um sistema não linear extraído da literatura, um modelo de suspensão veicular ativa para um quarto de carro. Neste sistema as não linearidades estão presentes no feixe de molas e no amortecedor. As condições de síntese foram programadas, simuladas e avaliadas em ambiente Matlab\textsuperscript{\textregistered}. Foram apresentados os resultados de simulação temporal e ao final é apresentada uma breve conclusão.
        \end{abstract}
        
        \selectlanguage{english}
        
        \begin{keyword} Linear systems; LTI; State feedback control; State Observer; Luenberger Observer; Vehicle active suspension;
        
        \vskip 1mm% não altere esse espaçamento
        \selectlanguage{brazil}
        {\noindent\it Palavras-chaves:} Sistemas lineares; LTI; Controle por realimentação de estados; Observador de estados; Observador de Luenberger; Suspensão ativa veicular;
        \end{keyword}
        
        \selectlanguage{brazil}
        
        \end{frontmatter}

    \section{Introdução}
        \input{content/introducao.tex}
    \section{Objetivos}
        \input{content/objetivos.tex}
    \section{Revisão Bibliográfica}
        \input{content/revisao_bibliografica.tex}
    \section{Metodologia}
        \input{content/metodologia.tex}
    \section{Resultados}
        \input{content/resultados.tex}
    \section{Conclusão}
        \input{content/conclusao.tex}
    \bibliography{references,manual}    
    \appendix
        \input{content/apendice.tex}   
\end{document}